Dynamic Modeling of the Human Coagulation Cascade using Reduced Order Effective Kinetic Models

### 2015-02-20 processes-69103_review_response/processes-69103.tex
Changes to discussion

A number of mathematical models and computational simulations concerning coagulation dynamics have been based on the Hockin-Mann model of coagulation.

>>>>

A number of mathematical models and computational simulations concerning coagulation dynamics have been based on the Hockin-Mann model of coagulation.  Recently, Brummel-Ziedins and co-workers built a model that incorporated the Protein C (PC) pathway into the Hockin-Mann network to investigate thrombin generation in cases of familial PC deficiency. Computational simulations using this model showed that PC mutation caused an elevation in peak thrombin levels without changing the initiation time or the slope of thrombin generation curve. Our hybrid model to a certain extent captured this trend qualitatively. We were able to show the decrease in peak thrombin concentration in the presence of PC pathway without any other inhibitors like ATIII. Mitrophanov et al. used kinetic modeling to study the effect of rfVIIa on thrombin generation. This study showed that increasing amounts of FVIIa accelerated the initiation phase and the propagation phase during thrombin generation. Analysis of thrombin generation curves showed that the FVIIa controlled the maximal slope of thrombin curve along with peak thrombin time and initiation time. Though we had issues in capturing the effect of FVIIa on initiation time we were able to show that change in concentration of FVIIa affected the maximal thrombin slope as well as propagation phase (Fig 7).
